---
title: "The New and Improved Iris Selector 2021"
author: "P.Y.Fong"
date: "`r format(Sys.Date(),'%d %B %Y')`"
output:
  ioslides_presentation:
    transition: slower
    logo: Lairis.jpg
    theme: cerulean
---

```{r setup, include=FALSE}
library (knitr)
opts_chunk$set(cache.lazy= T,
               echo = T,
               message=F,
               warning=F,
               comment="")
```

##      2.0 What is the Iris Selector?
###     The Iris Selector 2021 ;  

  - is a knowledge tool for discerning botanists.
  - provides fine distinctions between various species of Irises.
  - allows the user to view the essential measurements of the various Iris species available.
  - uses the highly accurate and recognized Iris data set containing 150 varieties of Irises.
  - was built based on cutting edge data science algorithms and tools.

##      3.0 Data Set Structure
The iris data set in all its "glory".
```{r data}
data <- iris
data <- data[,c(5,3:4,1:2)]
knitr::kable(head(data), 'html')
```

##      4.0 Variables Relationships
An overview of the variables and their relationships.
```{r plot}
plot(iris)
```

##      5.0 Availabilty  {data-background=northern-blue-iris.png data-background-size=400px data-background-position=right}

Click the link below to for your free access today!  
  
[Iris Selector 2021](https://pyfong.shinyapps.io/IrisSelector/)  
  
<div class="green">Hurry!  
Free for a limited timeonly.</div>  



Code available at [GitHub](http://github.com/pyfong1579/Coursera-Data-Science-Specialization_Course-8_Week-4-Project_Shiny-Application-Reproducible-Pitch.)  